---
title: "Approval Page for Stephanie"
author: "Brendan Hellweg"
date: "1/10/2021"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Document Summary

This document shares the text of the Mayor's transition agenda tracker in an easy-to-edit format for the Mayor's comms team while staying responsive to OPI's code. The following document contains every major line of text from the transition tracker divided by page. Please send revised text back directly underneath the section you would like to change (you can copy and paste the text if you like).

## Page Header

Below is the title of the web page:

```{r, echo=FALSE}
print(title)
```


Below is the text at the top lefthand corner of the page:
```{r, echo=FALSE}
print(text1)
```

## Priorities & Progress Tab

Below is the introduction to the progress table:

```{r, echo=FALSE}
print(text2)
```

## About This Initiative Tab

Below is the draft letter from Mayor Scott for your review:

```{r, echo=FALSE}
print(aboutus)
```

## Resources & Feedback Tab

Below are the links at the top of this tab:

```{r, echo=FALSE}
print(link1)
print(link2)
print(link3)
print(link4)
print(link5)
print(link6)
```


